
```{r}
setwd("C:/Ambarish/Practical Machine Learning")
```

Read the training data
```{r}
traindata <- read.csv("pml-training.csv")
```

Table of the classe variable of the training data
```{r}
table(traindata$classe)
```

Read the test data
```{r}
testdata <- read.csv("pml-testing.csv")
```

Remove the factor variables from the training data
```{r}
x <- grep("factor",sapply(traindata,class))

traindata.2 <- traindata[,-(x)]
```

Remove the columns where the column is NA
```{r}
traindata.3 <- traindata.2[, colSums(is.na(traindata.2)) == 0 ]
```

Include the classe variable in the training data
```{r}
traindata.3$classe <- traindata$classe
```

Remove the following variables from the data set
X
user_name
raw_timestamp_part_1    
raw_timestamp_part_2
```{r}
traindata.3 <- traindata.3[,5:57]
```

Ensure that the testdata has the same variables as that of the train data
```{r}
tesdata.1 <- testdata[,names(traindata.3[,1:52])]
```

Load the caret library
```{r}
library(caret)
```

Use cross validation with K =4
```{r}
trControl = trainControl(method = "cv", number = 4)
```

Use the randomForest algorithm to create the model
```{r}
modelFit <- train(traindata.3$classe ~ .,method="rf",data=traindata.3,trControl = trControl)
```

Predict the model
```{r}
predictions <- predict(modelFit,tesdata.1)
```

Create the function to create the files
```{r}
pml_write_files = function(x){
  n = length(x)
  for(i in 1:n){
    filename = paste0("problem_id_",i,".txt")
    write.table(x[i],file=filename,quote=FALSE,row.names=FALSE,col.names=FALSE)
  }
}
```

```{r}
setwd("C:/Ambarish/Practical Machine Learning/Answers")
```

```{r}
pml_write_files(predictions)
```


